Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

From the analyis above, it can be interpreted that the use of significant values on the PRA Engine will have an effect on the results, especially if the regression case to be detected does not
has a very significant change in its latency value as shown in
in the case of IS1. It can be concluded that the greater the significant value, the more sensitive the algorithm is in detecting regressions that occur because they don't
very strong evidence to reject $h_{0}$ but it means that $h_{0}$ cannot be rejected by too sure. Conversely, the smaller the significant value used, the smaller the value, the stronger the evidence needed to reject $h_{0}$ which means that $h_{0}$ can be rejected with more confidence.

>>>>

From the analyis above, it can be interpreted that the use of significant values on the PRA Engine will have an effect on the results, especially if the regression case to be detected does not
has a very significant change in its latency value as shown in
in the case of IS1. It can be concluded that the greater the significant value, the more sensitive the algorithm is in detecting regressions that occur because they don't
very strong evidence to reject $h_{0}$ but it means that $h_{0}$ cannot be rejected too confidently. Conversely, the smaller the significant value used, the smaller the value, the stronger the evidence needed to reject $h_{0}$ which means that $h_{0}$ can be rejected with more confidence.
